Excuse me, do you have a moment to talk about version control?

### 2017-05-13 README.Rmd
Move GitHub issues up; closes #5

In my opinion, **for new users**, the pros of Git only outweigh the cons when you factor in the overhead of communicating and collaborating with other people, including your future self. And who among us does not need to do that? Your life is much easier if this is baked into your workflow, as opposed to being a separate process that you dread and avoid. Communication and collaboration are the killer apps of version control. Git enforces a painfully rigorous model of file management, but it is critical for the distribution of files across different people, computers, and time.

Many people who don't use Git unwittingly re-invent a poor man's version of it. They take an important file and distribute it via email. All parties make changes, decorating the file name with initials, dates, and other descriptors. Before you know it, the original file is the root of a complicated phylogeny that no amount of "Track changes" and good intentions can resolve.

@@

This article does not provide step-by-step instructions on how to use Git and GitHub. This format would not be effective, but we do provide links to such resources. Instead, I'll convey what the workflow feels like and what the payoffs are. The goal is to help the Git-curious generate the activation energy needed to get started.

## GitHub

@@

@@

## Initial setup

@@

In addition to a well-designed user interface, GitHub offers two especially important features:

  * **Issues.** Remember how we're high-jacking software development tools? Well, this is the bug tracker. It's a list of things ... bugs, feature requests, to dos, whatever.
    - Issues are tightly integrated with email and therefore allow you to copy/embed important conversations in the associated repo.
    - Issues can be assigned to people (e.g., to dos) and tagged ("bug" or "progress-report").
    - Issues are tightly integrated with commits and therefore allow you to record *that the changes in this commit solve that problem which was discussed in that issue*.
    - As a new user of GitHub, one of the most productive things you can do is to use GitHub issues to provide a clear bug report or feature request for a package you use.
 * **Pull requests.** Git allows a project to have multiple, independent branches of development, with the notion that some should eventually be merged back into the main development branch. These are technical Git terms but hopefully also make sense on their own. A pull request is a formal proposal that says: "Here are some changes I would like to make." It might be linked to a specific issue: "Related to #14." or "Fixes #56". GitHub facilitates and preserves the discussion of the proposal, holistically and line-by-line.

>>>>

In my opinion, **for new users**, the pros of Git only outweigh the cons when you factor in the overhead of communicating and collaborating with other people, including your future self. And who among us does not need to do that? Your life is much easier if this is baked into your workflow, as opposed to being a separate process that you dread and avoid. Communication and collaboration are the killer apps of version control. Git enforces a rigorous model of file management, but it is critical for the distribution of files across different people, computers, and time.

Many people who don't use Git unwittingly re-invent a poor man's version of it. They take an important file and distribute it via email. Various parties make changes, decorating the file name with initials, dates, and other descriptors. Before you know it, the original file is the root of a complicated phylogeny that no amount of "Track changes" and good intentions can resolve.

@@

This article does not provide step-by-step instructions on how to use Git and GitHub. This format would not be effective, but we do provide links to such resources. Instead, I'll convey what the workflow feels like and what the payoffs are, with special attention to the statsitics and R context. The goal is to help the Git-curious generate the activation energy needed to get started.

## What is GitHub?

@@

GitHub __issues__ are another powerful feature of the platform. Recall that we are repurposing Git, a tool designed to facilitate software development. The issues for a project are its bug tracker. For projects that are not pure software development, we use this machinery to organize our to do list more generally. The basic unit is an issue and you can interact with them in two ways. First, issues are integrated into the project's web interface on GitHub, with a rich set of options for linking to project files and incremental changes. Second, issues and their associated comment threads appear in your email, just like regular messages (this can, of course, be configured). The result is that all correspondence about a project comes through your normal channels, but is also tracked inside the project itself, with excellent navigability and search capabilities.

Issues can be assigned to specific people and they can be labelled, e.g. "bug", "simulation-study", or "final-exam". Coupled with the ability to cross-link issues and the project files or file changes, you have extraordinary power to document why things have happened in the past and to organize what needs to happen in the future.

## Initial Git setup

@@

@@

 * **Pull requests.** Git allows a project to have multiple, independent branches of development, with the notion that some should eventually be merged back into the main development branch. These are technical Git terms but hopefully also make sense on their own. A pull request is a formal proposal that says: "Here are some changes I would like to make." It might be linked to a specific issue: "Related to #14." or "Fixes #56". GitHub facilitates and preserves the discussion of the proposal, holistically and line-by-line.
